Informing policy via dynamic models: Cholera in Haiti

### 2023-08-21 ms-plos.Rnw
Formatted the parameter table

\begin{tabular}{|l@{}|l@{}t@{}|l@{}t@{}|l@{}t@{}|}

@@

  & {\fixed $\muIR^{-1}=\Sexpr{myround(7/p1["gamma"],1)}$}

@@

  & {\fixed $\muIR^{-1}=\Sexpr{myround(365/h2_fit$h2_params["gamma"],1)}$}

@@

  & {\fixed $\muIR^{-1}=\Sexpr{myround(365/p3["gamma1"],1)}$ }

@@

  & {\fixed $\muEI^{-1}=\Sexpr{myround(7/p1["sigma"],1)}$}

@@

  & {\fixed $\muEI^{-1}=\Sexpr{myround(365/h2_fit$h2_params["gammaE"],1)}$}

@@

\multirow{2}{*}{Seasonality}
  & $\begin{array}{l}
    \hspace{-1mm} \transmission_{1:6}=(
      \Sexpr{myround(p1["beta1"],1)},
      \Sexpr{myround(p1["beta2"],1)},

@@

      \Sexpr{myround(p1["beta3"],1)},
      \Sexpr{myround(p1["beta4"],1)},
      \Sexpr{myround(p1["beta5"],1)},
      \Sexpr{myround(p1["beta6"],1)})
    \end{array}$
  & {\fixed \seasAmplitude=0.4}
  & $\seasAmplitude = \Sexpr{myround(p3s["lambdaR"],2)}$
  & \eqref{eq:model3:water} \\

@@

  & $\phaseParm = \Sexpr{myround(h2_fit$h2_params['phase'], 2)}^*$

@@

  & $r = \Sexpr{signif(p3s["r"],3)}$

@@

  Immunity (yr)
  & {\fixed $\muRS^{-1}=\Sexpr{myround(1/p1["alpha"]/52,1)}$}
  & \eqref{model1:RS}
    $\begin{array}{l}
    \muRS^{-1}= \Sexpr{signif(1/h2_fit$h2_params["sigma"],2)} \\
    {\fixed \omega_1^{-1} = \Sexpr{myround(1/h2_fit$h2_params["Omega1"],1)}} \\
    {\fixed \omega_2^{-1} = \Sexpr{myround(1/h2_fit$h2_params["Omega2"],1)}}
    \end{array}$
  & $\begin{array}{l}
    \eqref{model2:RS} \\
    \eqref{model2:omega1} \\
    \eqref{model2:omega1}
    \end{array} $
  & {\fixed $\muRS^{-1}=\Sexpr{myround(1/p3['rho1'],1)}$}
  & \eqref{eq:model3:RRnext}

@@

Birth/death (yr)
  & \fixed{$\begin{array}{l}
    \muBirth^{-1} = \Sexpr{myround(1/p1["mu"]/52,1)} \\
    \muDeath^{-1} = \Sexpr{myround(1/p1["delta"]/52,1)}
    \end{array}$}
  & {\fixed $\muDeath^{-1} = \Sexpr{myround(1/p3["mu1"],1)}$}
  & \eqref{eq:model3:IS}
  & {\fixed $\symptomFrac_z(t)=c\vaccineEfficacy^*(t-\tau_d)$}
  & {\fixed $\symptomFrac=\Sexpr{myround(h2_fit$h2_params["k"],1)}$}
  & {\fixed $\symptomFrac=\Sexpr{myround(p3["sigma1"],2)}$}
$\begin{array}{l}
\text{Asympt.} \\
\text{infectivity}
\end{array}$
  & {\fixed $\asymptomRelativeInfect=0.05$ }
  & $\begin{array}{l}
      {\fixed \asymptomRelativeInfect =0.001 } \\
      {\fixed \asymptomRelativeShed = \Sexpr{1e-7} }
    \end{array}$
  & \begin{tabular}{l}
      \eqref{model2:lambda} \\
      \eqref{model2:to_W}
    \end{tabular}
  &  $\begin{array}{l}
      {\fixed \asymptomRelativeInfect =1 } \\
      \asymptomRelativeShed = \Sexpr{myround(p3s["XthetaA"],3)}
    \end{array}$
  & \begin{tabular}{l}
      \eqref{eq:model3:foi} \\
      \eqref{eq:model3:water}
    \end{tabular}

@@

$\begin{array}{l}
\text{Human to}\\
\text{human}\end{array}$
  & $\transmission_{1:6}$ as above
  & $\transmission=$\Sexpr{signif(h2_fit$h2_params["Beta"],3)}
  & $\begin{array}{l}
      \hspace{-1mm} \transmission_{1:10}=(
        \Sexpr{myround(p3u["foi_add",1]*1e6,2)},
	\Sexpr{myround(p3u["foi_add",2]*1e6,2)},

@@

	\Sexpr{myround(p3u["foi_add",3]*1e6,2)},
        \Sexpr{myround(p3u["foi_add",4]*1e6,2)},
	\Sexpr{myround(p3u["foi_add",5]*1e6,2)},
	\Sexpr{myround(p3u["foi_add",6]*1e6,2)},
	\Sexpr{myround(p3u["foi_add",7]*1e6,2)},
	\Sexpr{myround(p3u["foi_add",8]*1e6,2)},
	\Sexpr{myround(p3u["foi_add",9]*1e6,2)},
	)
      \times 10^{-6}
    \end{array}$

@@

$\begin{array}{l}
\text{Water to}\\ \text{human}
\end{array}$
  & $\begin{array}{l}
    {\fixed \Wsat = \Sexpr{signif(h2_fit$h2_params["Sat"],2)} }
    \beta_W= \Sexpr{signif(h2_fit$h2_params["BetaW"],3)}
    \end{array}$
  & $\begin{array}{l}
      \hspace{-1mm} \Wbeta{_{1:10}}= (
        \Sexpr{myround(p3u["betaB",1],2)}, \Sexpr{myround(p3u["betaB",2],2)},
        \Sexpr{myround(p3u["betaB",3],2)}, \Sexpr{myround(p3u["betaB",4],2)},
        \Sexpr{myround(p3u["betaB",5],2)}, \Sexpr{myround(p3u["betaB",6],2)},
        \Sexpr{myround(p3u["betaB",7],2)}, \Sexpr{myround(p3u["betaB",8],2)},
        \Sexpr{myround(p3u["betaB",9],2)}, \Sexpr{myround(p3u["betaB",10],2)}
      ) \end{array}$
$\begin{array}{l}
\text{Human to}\\
\text{water}\end{array}$

@@

$\begin{array}{l}
\text{Water} \\
\text{survival (wk)}
\end{array}$

@@

  & {\fixed $\Wremoval^{-1} = $ \Sexpr{signif(52/h2_fit$h2_params["Delta"],3)}}

@@

@@

$\begin{array}{l}
\text{Process} \\
\text{noise} (\text{wk}^{1/2})
\end{array}$
  & $\sigmaProc=(\Sexpr{myround(sqrt(p1["sig_sq_epi"]),2)}, \Sexpr{myround(sqrt(p1["sig_sq_end"]),2)})^*$

@@

  & $\sigmaProc= \Sexpr{myround(p3s["std_W"],3)}$

@@

  & (S15)
  & {\fixed $\reportRate=\Sexpr{myround(h2_fit$h2_params["Rho"],2)}$}
  & (S16)

@@

  & (S19)

@@

$\begin{array}{l}
\text{Observation} \\
\text{variance}
\end{array}$
  & $\obsOverdispersion = (\Sexpr{myround(p1["tau_epi"],2)}, \Sexpr{round(p1["tau_end"],2)})$
  & (S15)
  & $\obsOverdispersion = \Sexpr{signif(h2_fit$h2_params['sigma'], 3)}$
  & (S16)
  & $\obsOverdispersion = \Sexpr{myround(p3s["k"],2)}$
  & (S19)

@@

\multirow{2}{*}{Initial Values} & $I_{0,0} = \Sexpr{round(prod(p1[c('pop_0', 'I_0')]))}$ & & \multicolumn{1}{c}{\multirow{2}{*}{\hspace{16pt}\missing}} & & \multirow{2}{*}{$I_{3,7,10;0}(0)= (
        \Sexpr{round(prod(p3[c('H3', 'Iinit3')]))}, \Sexpr{round(prod(p3[c('H7', 'Iinit7')]))}, \Sexpr{round(prod(p3[c('H10', 'Iinit10')]))})^*$} & \\
& $E_{0,0} = \Sexpr{round(prod(p1[c('pop_0', 'E_0')]))}$ & & \multicolumn{1}{c}{} & & & \\\hline
Hurricane & \multicolumn{1}{c}{\multirow{2}{*}{\hspace{16pt}\missing}} & & \multicolumn{1}{c}{\multirow{2}{*}{\hspace{16pt}\missing}} & & $\Whur{3, 9} = (\Sexpr{myround(p3['aHur3'], 2)}, \Sexpr{myround(p3['aHur9'], 2)})^*$ & \multirow{2}{*}{\eqref{eq:model3:foi}} \\
Parameters & \multicolumn{1}{c}{} & & \multicolumn{1}{c}{} & & $\hHur{3, 9} = (\Sexpr{myround(p3['hHur3'], 2)}, \Sexpr{myround(p3['hHur9'], 2)})^*$ & \\\hline

>>>>

\begin{tabular}{|p{0.15\linewidth}|p{0.14\linewidth}t|p{0.13\linewidth}t|p{0.17\linewidth}t|}

@@

  & ${\fixed \muIR^{-1}=\Sexpr{myround(7/p1["gamma"],1)}}$

@@

  & ${\fixed \muIR^{-1}=\Sexpr{myround(365/h2_fit$h2_params["gamma"],1)}}$

@@

  & ${\fixed \muIR^{-1}=\Sexpr{myround(365/p3["gamma1"],1)}}$

@@

  & ${\fixed \muEI^{-1}=\Sexpr{myround(7/p1["sigma"],1)}}$

@@

  & ${\fixed \muEI^{-1}=\Sexpr{myround(365/h2_fit$h2_params["gammaE"],1)}}$

@@

\multirow{3}{*}{Seasonality}
  & $\transmission_{1:6}=(
      \Sexpr{myround(p1["beta1"],1)},\allowbreak
      \Sexpr{myround(p1["beta2"],1)},\allowbreak
      \Sexpr{myround(p1["beta3"],1)},\allowbreak
      \Sexpr{myround(p1["beta4"],1)},\allowbreak
      \Sexpr{myround(p1["beta5"],1)},\allowbreak
      \Sexpr{myround(p1["beta6"],1)})$
  & \multirow{2}{*}{${\fixed \seasAmplitude=0.4}$}
  & \multirow{2}{*}{\eqref{model2:lambda}}
  & \multirow{2}{*}{$\seasAmplitude = \Sexpr{myround(p3s["lambdaR"],2)}$}
  & \multirow{2}{*}{\eqref{eq:model3:water}}

@@

@@

  & \multirow{-2}{*}{$\phaseParm = \Sexpr{myround(h2_fit$h2_params['phase'], 2)}^*$}
  & \multirow{-2}{*}{\eqref{model2:lambda}}
  & \multirow{-2}{*}{$\rainfallExponent = \Sexpr{signif(p3s["r"],3)}$}
  & \multirow{-2}{*}{\eqref{eq:model3:water}}
  \multirow{3}{*}{Immunity (yr)}
  & \multirow{3}{*}{${\fixed \muRS^{-1}=\Sexpr{myround(1/p1["alpha"]/52,1)}}$}
  & \multirow{3}{*}{\eqref{model1:RS}}
  & $\muRS^{-1}= \Sexpr{signif(1/h2_fit$h2_params["sigma"],2)}$
  & \eqref{model2:RS}
  & \multirow{3}{*}{${\fixed \muRS^{-1}=\Sexpr{myround(1/p3['rho1'],1)}}$}
  & \multirow{3}{*}{\eqref{eq:model3:RRnext}}
& & & ${\fixed \omega_1^{-1} = \Sexpr{myround(1/h2_fit$h2_params["Omega1"],1)}}$ & \eqref{model2:omega1} & &\\
& & & ${\fixed \omega_2^{-1} = \Sexpr{myround(1/h2_fit$h2_params["Omega2"],1)}}$ & \eqref{model2:omega2} & &\\
\multirow{2}{*}{Birth/death (yr)}
  & ${\fixed \muBirth^{-1} = \Sexpr{myround(1/p1["mu"]/52,1)}}$
    %
  & \multirow{2}{*}{\missing}
  & \multirow{2}{*}{${\fixed \muDeath^{-1} = \Sexpr{myround(1/p3["mu1"],1)}}$}
  & \multirow{2}{*}{\eqref{eq:model3:IS}}
& ${\fixed \muDeath^{-1} = \Sexpr{myround(1/p1["delta"]/52,1)}}$
& &
  & ${\fixed \symptomFrac_z(t)=c\vaccineEfficacy^*(t-\tau_d)}$
  & ${\fixed \symptomFrac=\Sexpr{myround(h2_fit$h2_params["k"],1)}}$
  & ${\fixed \symptomFrac=\Sexpr{myround(p3["sigma1"],2)}}$
Asympt.
  & \multirow{2}{*}{${\fixed \asymptomRelativeInfect=0.05}$}
  & \multirow{2}{*}{\eqref{model1:lambda}}
  & ${\fixed \asymptomRelativeInfect = 0.001}$

@@

  &  ${\fixed \asymptomRelativeInfect = 1}$
infectivity
& ${\fixed \asymptomRelativeShed = \Sexpr{1e-7} }$
& $\asymptomRelativeShed = \Sexpr{myround(p3s["XthetaA"],3)}$

@@

@@

\multirow{4}{*}{Human to human}
  & \multirow{4}{*}{$\transmission_{1:6}$ as above}
  & \multirow{4}{*}{\eqref{model1:lambda}}
  & \multirow{4}{*}{$\transmission=$\Sexpr{signif(h2_fit$h2_params["Beta"],3)}}
  & \multirow{4}{*}{\eqref{model2:lambda}}
  & $\transmission_{1:10}=(
  \Sexpr{myround(p3u["foi_add",1]*1e6,2)}, \allowbreak
	\Sexpr{myround(p3u["foi_add",2]*1e6,2)}, \allowbreak
	\Sexpr{myround(p3u["foi_add",3]*1e6,2)}, \allowbreak
  \Sexpr{myround(p3u["foi_add",4]*1e6,2)}, \allowbreak
	\Sexpr{myround(p3u["foi_add",5]*1e6,2)}, \allowbreak
	\Sexpr{myround(p3u["foi_add",6]*1e6,2)}, \allowbreak
	\Sexpr{myround(p3u["foi_add",7]*1e6,2)}, \allowbreak
	\Sexpr{myround(p3u["foi_add",8]*1e6,2)}, \allowbreak
	\Sexpr{myround(p3u["foi_add",9]*1e6,2)}, \allowbreak
	) \allowbreak \times 10^{-6}$
  & \multirow{4}{*}{\eqref{eq:model3:foi}}

@@

\multirow{5}{*}{Water to human}
  & \multirow{5}{*}{\missing}
  % & \multicolumn{1}{c}{\hspace{16pt}\missing}
  & \multirow{3}{*}{${\fixed \Wsat = \Sexpr{signif(h2_fit$h2_params["Sat"],2)}}$}
  & \multirow{3}{*}{\eqref{model2:lambda}}
  % \eqref{model2:lambda}
  & $\Wbeta{_{1:10}}= (
        \Sexpr{myround(p3u["betaB",1],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",2],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",3],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",4],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",5],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",6],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",7],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",8],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",9],2)}, \allowbreak
        \Sexpr{myround(p3u["betaB",10],2)})$
  & \multirow{4}{*}{\eqref{eq:model3:foi}}

@@

& & & \multirow{-3}{*}{$\beta_W= \Sexpr{signif(h2_fit$h2_params["BetaW"],3)}$} & \multirow{-3}{*}{\eqref{model2:lambda}} & &

@@

Human to water
  & \missing
  % & \multicolumn{1}{c}{\hspace{16pt}\missing}

@@

Water survival \newline (wk)
  & \missing
  % & \multicolumn{1}{c}{\hspace{16pt}\missing}

@@

  & ${\fixed \Wremoval^{-1} = \Sexpr{signif(52/h2_fit$h2_params["Delta"],3)}}$

@@

  & \missing
  % & \multicolumn{1}{c}{\hspace{16pt}\missing}

@@

Process noise \newline ($\text{wk}^{1/2}$)
  & $\sigmaProc =$ \newline $(\Sexpr{myround(sqrt(p1["sig_sq_epi"]),2)},
  \Sexpr{myround(sqrt(p1["sig_sq_end"]),2)})^*$
  & \multirow{2}{*}{\eqref{model1:lambda}}
  & \multirow{2}{*}{\missing}
  % & \multicolumn{1}{c}{\hspace{16pt}\missing}

@@

  & \multirow{2}{*}{$\sigmaProc= \Sexpr{myround(p3s["std_W"],3)}$}
  & \multirow{2}{*}{\eqref{eq:model3:SA}}

@@

  & (S15) % TODO: Check
  & ${\fixed \reportRate=\Sexpr{myround(h2_fit$h2_params["Rho"],2)}}$
  & (S16) % TODO: Check

@@

  & (S19) % TODO: Check

@@

Observation variance
  & $\obsOverdispersion =$ \newline $(\Sexpr{myround(p1["tau_epi"],2)}, \Sexpr{round(p1["tau_end"],2)})$
  & \multirow{2}{*}{(S15)} % TODO: Check
  & \multirow{2}{*}{$\obsOverdispersion = \Sexpr{signif(h2_fit$h2_params['sigma'], 3)}$}
  & \multirow{2}{*}{(S16)} % TODO: Check
  & \multirow{2}{*}{$\obsOverdispersion = \Sexpr{myround(p3s["k"],2)}$}
  & \multirow{2}{*}{(S19)} % TODO: Check

@@

\multirow{2}{*}{Initial Values} & $I_{0,0} = \Sexpr{round(prod(p1[c('pop_0', 'I_0')]))}$
  & \multirow{2}{*}{\missing}
  % & \multicolumn{1}{c}{\multirow{2}{*}{\hspace{16pt}\missing}}
  & \multirow{2}{*}{$I_{3,7,10;0}(0)= (
        \Sexpr{round(prod(p3[c('H3', 'Iinit3')]))}, \Sexpr{round(prod(p3[c('H7', 'Iinit7')]))}, \Sexpr{round(prod(p3[c('H10', 'Iinit10')]))})^*$}
  &  % TODO: \multirow{2}{*}{EQUATION NUMBER}
  & $E_{0,0} = \Sexpr{round(prod(p1[c('pop_0', 'E_0')]))}$ & & \multicolumn{1}{c}{}
\multirow{3}{*}{Hurricane}
  & \multirow{4}{*}{\missing}
% & \multicolumn{1}{c}{\multirow{2}{*}{\hspace{16pt}\missing}}
  & \multirow{4}{*}{\missing}
  % & \multicolumn{1}{c}{\multirow{2}{*}{\hspace{16pt}\missing}}
  & $\Whur{3, 9} =$\newline $(\Sexpr{myround(p3['aHur3'], 2)}, \Sexpr{myround(p3['aHur9'], 2)})^*$
  & \multirow{2}{*}{\eqref{eq:model3:foi}}
 \multirow{-1}{*}{Parameters} &
  % & \multicolumn{1}{c}{}
  % & \multicolumn{1}{c}{}
  & $\hHur{3, 9} =$\newline $(\Sexpr{myround(p3['hHur3'], 2)}, \Sexpr{myround(p3['hHur9'], 2)})^*$
  & \multirow{2}{*}{\eqref{eq:model3:foi}}
